---
title: "Homework 9 R Package"
author: "Anh Khoa Vo"
date: "23rd November 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package was created as a requirement for Homework 9 in Stats 547:

In the package Power, I have several functions including: square, reciprocal, and box-cox transformation. In addition, I have special function in the package such as linking character together.  

For example: 

1. If you would like to square some numbers, I have a square function:
```{r}
library(Powers)
x <- square(10)
x
```

2. If you would like to reciprocal some number, I have a reciprocal function:
```{r}
x <- reciprocal(10)
x
```

3. If you would like to transform some numers, I have the box-cox function: 

In the case lambda is not 0:
```{r}
x <- boxcox(10,3)
x
```

In the case lambda is 0: 
```{r}
x <- boxcox(10,0)
x
```

4. The reverse box-cox transformation:

In the case lambda is not 0:
```{r}
x <- reverse_boxcox(10,3)
x
```

In the case lambda is 0:
```{r}
x <- reverse_boxcox(10,0)
x
```


5. For special function in this homework, I created the link function:
```{r}
x <- c("Anh", "Khoa", "Vo")
y <- link(x)
y
```

Thank you!!!
